Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2024-11-27 02_paper/02_study/02_expertise_paper/expertise_2024_11_18_MK.Rmd
x paper

# Data Import and Preparation --------------------------------------------
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  dplyr::select(
    LI06_05, 
    LM01_01:LM01_08,  # Classroom Management
    LP01_01:LP01_08   # Non-/Paraverbal Communication
  ) %>%
  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
  mutate(Group = ifelse(LI06_05 < 200, "Novice", "Expert")) %>%  # Group Definition
  select(-LI06_05) %>%  # Drop ID column
  na.omit()  # Remove NAs

# Summary Statistics Table -----------------------------------------------
df_quest_table <- df_quest %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    `M cm` = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
    `SD cm` = round(sd(c_across(starts_with("LM")), na.rm = TRUE), 2),
    `Min cm` = round(min(c_across(starts_with("LM")), na.rm = TRUE), 2),
    `Max cm` = round(max(c_across(starts_with("LM")), na.rm = TRUE), 2),
    `M n&pv com` = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2),
    `SD n&pv com` = round(sd(c_across(starts_with("LP")), na.rm = TRUE), 2),
    `Min n&pv com` = round(min(c_across(starts_with("LP")), na.rm = TRUE), 2),
    `Max n&pv com` = round(max(c_across(starts_with("LP")), na.rm = TRUE), 2)
  )

# Display APA-Conform Table
kable(df_quest_table, 
      caption = "Summary Statistics for Classroom Management and Non-/Paraverbal Communication") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = FALSE)

# Create Dataset for Plotting --------------------------------------------
df_quest_long <- df_quest %>%
  rowwise() %>%
  transmute(
    Group = Group,
    All = round(mean(c_across(starts_with("L")), na.rm = TRUE), 2),
    `Classroom Management` = round(mean(c_across(starts_with("LM")), na.rm = TRUE), 2),
    `Non-/Paraverbal Communication` = round(mean(c_across(starts_with("LP")), na.rm = TRUE), 2)
  ) %>%
  ungroup() %>%
  pivot_longer(!Group, names_to = "Scales Self-evaluation", values_to = "Mean")

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )

>>>>

# Data Import and Preparation --------------------------------------------
df_quest <- read_excel("./data/data_empschul_labor_lehrperson.xlsx") %>%
  filter(LI06_05 != 201, LI06_05 != 223) %>%  # Exclude specific IDs
  mutate(
    Group = ifelse(LI06_05 < 200, "Novice", "Expert"),  # Group Definition
    Participant = LI06_05  # Add new column "Participant"
  ) %>%
  arrange(Participant) %>% 
  select(
    Participant, 
    Group, 
    LM01_01:LM01_05,  # Classroom Management
    LM01_06:LM01_08,  # Disruption Handling
    LP01_01:LP01_08   # Presence
  ) %>%
  rename(
    CM_01 = LM01_01, CM_02 = LM01_02, CM_03 = LM01_03, CM_04 = LM01_04, CM_05 = LM01_05,
    DH_01 = LM01_06, DH_02 = LM01_07, DH_03 = LM01_08,
    P_01 = LP01_01, P_02 = LP01_02, P_03 = LP01_03, P_04 = LP01_04, P_05 = LP01_05,
    P_06 = LP01_06, P_07 = LP01_07, P_08 = LP01_08
  ) %>%
  na.omit()  # Remove NAs

# Create Dataset for Plotting --------------------------------------------
df_quest_long <- df_quest %>%
  rowwise() %>%
  transmute(
    Group = Group,
    `Classroom Management` = round(mean(c_across(starts_with("CM")), na.rm = TRUE), 2),
    `Disruption Handling` = round(mean(c_across(starts_with("DH")), na.rm = TRUE), 2),
    `Presence` = round(mean(c_across(starts_with("P") & !starts_with("Participant")), na.rm = TRUE), 2)  # Excluding Participant column
  ) %>%
  ungroup() %>%
  pivot_longer(!Group, names_to = "Scales Self-evaluation", values_to = "Mean")

# Plot Mean Scores by Group ----------------------------------------------
quest_plot <- df_quest_long %>%
  mutate(Group = factor(Group, levels = c("Novice", "Expert"))) %>%
  ggplot(aes(x = Group, y = Mean)) +
  geom_boxplot(aes(fill = Group), outlier.shape = NA) +
  geom_point(
    size = 1,
    alpha = 0.4,
    position = position_jitter(seed = 1, width = 0.1, height = 0.1)
  ) +
  labs(x = "", y = "Mean Scores") +
  ylim(0, 4) + 
  scale_fill_brewer(palette = "RdBu") +
  facet_wrap(~`Scales Self-evaluation`, nrow = 1, strip.position = "bottom") +
  theme_cowplot() +
  ggtitle("Self-Evaluation Scores") +
  theme(
    plot.title = element_text(size = 25, face = "bold"),
    legend.title = element_text(size = 20),
    legend.text = element_text(size = 15),
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.title.y = element_text(size = 20)
  )
